---
title: "Final Project"
author: "Maida Ismail"
date: "2024-12-01"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readxl)
library(ggplot2)
library(plotly)
library(tm)
library(tidyverse)
```

$\mu_{Yes}$: Mean of sleep hours on the days I went to the gym.
$\mu_{No}$: Mean of sleep hours on the days I did not go to the gym.

$H_0: \mu_{Yes} <= \mu_{No}$
$H_A: \mu_{Yes} > \mu_{No}$

```{r}
url = "~/OneDrive - Minnesota State/Desktop/Data 211/FinalProjectData.xltx"
data = read_excel(url)

t.test(data$`Sleep hrs`~ data$`Go to the gym?`, alternative = "greater")
```
Since the p-value is 0.5604 which is greater than the significance level $\alpha=0.05$ , I fail to reject the null hypothesis. That means there is not enough evidence to support the claim that the average hours of sleep on the days I went to the gym is significantly higher than the days I did not visit the gym.

\newpage

# A bar graph to show the mean
```{r}
mean_data = data %>%
  group_by(`Go to the gym?`) %>%
  summarize(
    mean_by_sleep = mean(`Sleep hrs`, na.rm = TRUE)
  )

graph = ggplot(mean_data, aes(x = `Go to the gym?`, y = mean_by_sleep)) +
  geom_bar(stat = "identity", fill = "orchid") +
  labs(x = "Did I go to the gym?", y = "Average Sleep Hour", title = "Comparison of Sleep Hours Based on Gym Attendance") 


ggplotly(graph)
```


\newpage

# A bar graph with error bars
```{r}
mean_data = data %>%
  group_by(`Go to the gym?`) %>%
  summarize(
    mean_by_sleep = mean(`Sleep hrs`, na.rm = TRUE),
    se_sleep = sd(`Sleep hrs`, na.rm = TRUE) / sqrt(n())
  )

graph = ggplot(mean_data, aes(x = `Go to the gym?`, y = mean_by_sleep)) +
  geom_bar(stat = "identity", fill = "orchid") +
  labs(x = "Did I go to the gym?", y = "Average Sleep Hour", title = "Comparison of Sleep Hours Based on Gym Attendance") +
  geom_errorbar(aes(ymin = mean_by_sleep - se_sleep, ymax = mean_by_sleep + se_sleep), width = 0.2)


ggplotly(graph)
```




